---
title: "Automative Reporting Weedmon"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

## Download necessary packages if not downloaded
## 
```{r}
# if these packages aren't installed use install.packages("package name")
library(tidyverse)
library(readxl)
library(here)
library(dplyr)
library(ggplot2)
library(ggrepel)
library(kableExtra)
library(knitr)
library(DT)

```

*Note install/if not use code below*

install.packages(c("tidyverse", "readxl", "here", "dplyr", "ggplot2", "ggrepel", "DT", "knitr"))

devtools::install_github("haozhu233/kableExtra")

# SET YEAR
```{r}
# Setting this variable to the year will produce the correct code for the year you would like
year_code <- 2022

```


Set Working Directory
*Occasionally on Windows R Markdown has trouble finding directory, specified full file path location in read_excel file can use setwd() if working*

# File Notes
Files that do change
ACCESS:
qry_2020_DRT_CountOfNNIS_perTransect2.xlsx
SAMO's 25 Target Invasive Species.xlsx

ARCGIS:
raw_POE_WeedSurveyLn_2016to2020.xlsx
raw_POE_WeedSurveyLn_2016to2020.xlsx

Files that Don't change year to year
POE_WeedSurveyLn&Pt_2016to2020.xlsx

# Format excel sheets and clean

Making the clean excel files
```{r}
# DRT
# Specified full directory

# 2021 from Github
DRT_NNIS_raw <- read_excel(here(file = "qry_2021_DRT_CountOfNNIS_perTransect2.xlsx"))
# make dataframe
DRT_NNIS_raw <- data.frame(DRT_NNIS_raw)

# 2022 File Format from Survey123
DRT_species_table <- read.csv(file="tbl_Species_1_2022_test.csv")
DRT_data_entry <- read.csv(file="MEDN_DRT_Data_Entry_v_2_0._2022_test.csv")

# DRT Species Table has SpeciesName = Target.Species, SubTransect, ParentGlobalID
# DRT_data_entry has Site_ID = Loc_Name, Location_ID = Location_Code, GlobalID
DRT_species_table <- select(DRT_species_table, Target.Species, SubTransect, ParentGlobalID)
DRT_species_table<- rename(DRT_species_table, SpeciesName = Target.Species, X = SubTransect, key = ParentGlobalID)
DRT_data_entry <- select(DRT_data_entry, Location_ID, GlobalID, Site_ID)
DRT_data_entry <- rename(DRT_data_entry, Loc_Name = Site_ID, Location_Code = Location_ID, key = GlobalID)

# Join data
DRT_survey <- right_join(DRT_data_entry, DRT_species_table)
DRT_survey$SurveyYear <- year_code
DRT_survey <- select(DRT_survey, -key)

# Need to ask about NAs but for now lets remove them and pivot
DRT_survey <- na.omit(DRT_survey)

DRT_survey$Found <- "X"

DRT_survey <- pivot_wider(DRT_survey, names_from = X, values_from = Found)

# if all subtransects have none then an X in the X0 column



####################################################################################################

# POE
# Pt
# Fields to keep: Shape, PARK_UNIT, SCNTFC_CD, SCNTFC_CD2, SCNTFC_CD3, SCNTFC_CD4, SCNTFC_CD5, BUFFER rev_M
poe_pt_raw <- read_excel(here(file = "raw_POE_WeedSurveyPt_2021.xlsx"))
# Keep certain columns
poe_pt_raw <- select(poe_pt_raw, Shape, PARK_UNIT, SCNTFC_CD, SCNTFC_CD2, SCNTFC_CD3, SCNTFC_CD4, SCNTFC_CD5, BUFFER_M, BEGIN_DT, LOC_NM, MEDN_Zone)
poe_pt_raw$year <- substr(poe_pt_raw$BEGIN_DT, 1, 4)
poe_pt_raw <- select(poe_pt_raw, -BEGIN_DT)
poe_pt_raw <- filter(poe_pt_raw, year == year_code)
poe_pt_raw <- filter(poe_pt_raw, PARK_UNIT == "SAMO")

# Correct Buffer
poe_pt_raw <- mutate(poe_pt_raw, buffer_rev = ifelse(BUFFER_M < .25, .5, BUFFER_M))
poe_pt_raw <- select(poe_pt_raw, - BUFFER_M)

# Calculate Area
poe_pt_raw$Area <- pi*(poe_pt_raw$buffer_rev^2)

# Line
# Fields to Keep: Shape, PARK_UNIT, SCNTFC_CD, SCNTFC_CD2, SCNTFC_CD3, SCNTFC_CD4, SCNTFC_CD5, LOC_NM
poe_ln_raw <- read_excel(here(file = "raw_POE_WeedSurveyLn_2021.xlsx"))
# poe_ln_raw <- rename(poe_ln_raw, Shape = `Shape *`)
poe_ln_raw <- select(poe_ln_raw, Shape, PARK_UNIT, SCNTFC_CD, SCNTFC_CD2, SCNTFC_CD3, SCNTFC_CD4, SCNTFC_CD5, BUFFER_M, BEGIN_DT, st_length_, Shape__L_3, LOC_NM, BUFDIR, MEDN_Zone)
# Make the 0s = NA
# Note: May be able to skip this step, in 2020 all lengths were under Shape__L_2
# or may need to change field name in source Excel file from "Shape__Len" to "Shape__L_3"
poe_ln_raw <- rename(poe_ln_raw, len1 = st_length_, len2 = Shape__L_3)
poe_ln_raw$len1 <- na_if(poe_ln_raw$len1, 0)
poe_ln_raw$len2 <- na_if(poe_ln_raw$len2, 0)
poe_ln_raw$len1 <- poe_ln_raw$len1*10^5
poe_ln_raw$len2 <- poe_ln_raw$len2*10^5
poe_ln_raw <- mutate(poe_ln_raw, length = coalesce(len1, len2))
# subset by year and park
poe_ln_raw$year <- substr(poe_ln_raw$BEGIN_DT, 1, 4)
poe_ln_raw <- select(poe_ln_raw, -BEGIN_DT, - len1, -len2)
poe_ln_raw <- filter(poe_ln_raw, year == year_code)
poe_ln_raw <- filter(poe_ln_raw, PARK_UNIT == "SAMO")

# Calculate Area
# first change BUFDIR to numeric
poe_ln_raw$BUFNUM <- as.numeric(gsub("LEFT", 1, gsub("RIGHT", 1, gsub("FULL", 2, poe_ln_raw$BUFDIR))))
poe_ln_raw$Area<- poe_ln_raw$BUFFER_M*poe_ln_raw$BUFNUM*poe_ln_raw$length

# Join the Line and Point Data
poe_ln_raw <- select(poe_ln_raw, LOC_NM, Shape, MEDN_Zone, SCNTFC_CD, SCNTFC_CD2, SCNTFC_CD3, SCNTFC_CD4,SCNTFC_CD5, Area)
poe_pt_raw <- select(poe_pt_raw, LOC_NM, Shape, MEDN_Zone, SCNTFC_CD, SCNTFC_CD2, SCNTFC_CD3, SCNTFC_CD4,SCNTFC_CD5, Area)

# Clean file
poe_clean <- full_join(poe_ln_raw, poe_pt_raw)

# Make all uppercase
poe_clean$LOC_NM <- toupper(poe_clean$LOC_NM)

```


Making POE Location Key for table A-1
*Need to locate clean sheet from 2016-2020 only used for POE names*
```{r}
# Using clean sheet only for this section 
poe_loc_key <- read_excel(here(file = "POE_WeedSurveyLn&Pt_2016to2020.xlsx"), sheet = 3)
poe_loc_key <- na.omit(unique(select(poe_loc_key, "POE #", "Location")))
poe_loc_key <- rename(poe_loc_key, poe = "POE #")

```


# Make Clean SPP record for POE
```{r}
# pivot data to make into more rows from each species record
poe_clean_pivot <- poe_clean
poe_clean_pivot <- rename(poe_clean_pivot, SCNTFC_CD1 = SCNTFC_CD)

poe_clean_pivot <- pivot_longer(poe_clean_pivot,
    cols = starts_with("SCNTFC_CD"),
    names_to = "SPP_Num",
    values_to = "spp",
    names_prefix = "SCNTFC_CD")

poe_clean_pivot <- na.omit(poe_clean_pivot)

```


# Create Species Key from 2 letter/3 letter/ full name
```{r}
spp_key <- read_excel(here(file = "SAMO's 25 Target Invasive Species.xlsx"), sheet=2, col_names = c("Scientific_name", "common_name", "six_let", "four_let", "USDA"), skip = 4)
spp_key <- select(spp_key, -common_name)

```


# Notes
MEDN_Zone:
Zone 1 = 1
Zone 2 = 2
Both = 3

when doing species combine to only have unique species no duplicates

POE Name = LOC_NM
if doesn't have name then remove

Do for point
Buffer_rev = default distance is .01 
replace all .01 with .5
Anything less then .25 make .5

if/then statement for zone 1, zone 2 or both

Point
zone 1 or zone 2 area = pi*buffer^2
Line
Buffer Distance in Meters* Length_m(Ln) * Buffer multiplier

For Length_m(Ln)
combine st_length_ and Shape__L_3
make 0 = NA
10^5 power for st_length
Shape__L_2 is the correct value

Buffer multiplier = 
BUFFDIR
FULL = 2
LEFT or RIGHT = 1

Buffer Distance in Meters = BUFFER_M





# Results

### Table 3 in report 
```{r}
# POE Spp per site
spp_obs_site <- group_by(poe_clean_pivot, LOC_NM, spp)
spp_obs_site <- summarise(spp_obs_site, Nsites = n())
spp_obs_site <- ungroup(spp_obs_site)
spp_obs_site<- group_by(spp_obs_site, spp)
spp_obs_site<- summarise(spp_obs_site, nsites= n())
spp_obs_site$pct <- round(spp_obs_site$nsites/sum(spp_obs_site$nsites) *100, 2)
spp_site_poe <- spp_obs_site
spp_site_poe <- rename(spp_site_poe, Species = spp)
spp_key_a1 <- select(spp_key, USDA, six_let)
spp_key_a1 <- rename(spp_key_a1, Species = USDA)
spp_site_poe <- right_join(spp_site_poe, spp_key_a1)
spp_site_poe <- select(spp_site_poe, -Species)
spp_site_poe <- na.omit(rename(spp_site_poe, Species = six_let, nsites_poe = nsites, pct_poe = pct))

# DRT Spp per site
spp_site_drt <- group_by(DRT_NNIS_raw, SpeciesName)
spp_site_drt <- summarize(spp_site_drt, nspp = n())
spp_site_drt$pct <- round(spp_site_drt$nspp/sum(spp_site_drt$nspp)*100, 2)
spp_site_drt <- rename(spp_site_drt, Species = SpeciesName, nsites_drt = nspp, pct_drt = pct)

# Join
spp_site_full <- right_join(spp_site_drt, spp_site_poe)

# Make NAs 0 so we can add
spp_site_full[is.na(spp_site_full)]=0

spp_site_full$tot_pct <- spp_site_full$pct_drt + spp_site_full$pct_poe
spp_site_full$tot_sites <- spp_site_full$nsites_drt + spp_site_full$nsites_poe

spp_site_full <- select(spp_site_full, Species, nsites_poe, nsites_drt, tot_sites, pct_poe, pct_drt, tot_pct)

spp_site_full_dt <- datatable(spp_site_full)

spp_site_full_dt

```


## Points of Entry

### Table A-1: group by location, scientific name, zone, area for each species per site
*Need to locate clean sheet from 2016-2020 for POE names*
```{r}
# Make Location Key, using clean sheet only for this section 
poe_loc_key <- read_excel(here(file = "POE_WeedSurveyLn&Pt_2016to2020.xlsx"), sheet = 3)
poe_loc_key <- na.omit(unique(select(poe_loc_key, "POE #", "Location")))
poe_loc_key <- rename(poe_loc_key, LOC_NM = "POE #")

# Create table
tablea1 <- group_by(poe_clean_pivot, LOC_NM, MEDN_Zone, spp)
tablea1 <- summarise(tablea1, sumarea = sum(Area))
tablea1$MEDN_Zone <- as.character(gsub(1, "Hardscape or Trail", gsub(2, "Buffer", gsub(3, "Border", tablea1$MEDN_Zone))))

# for later before getting rid of species
tablea2 <- tablea1

# join key to pivot table
tablea1 <- right_join(tablea1, poe_loc_key)
tablea1 <- select(tablea1, LOC_NM, Location, spp, sumarea, MEDN_Zone)
tablea1 <- rename(tablea1, "POE#" = LOC_NM, Species = spp, "Gross Area Infested (sq. m)" = sumarea, Zone = MEDN_Zone)

# key from USDA to 6 letter code
tablea1 <- right_join(spp_key_a1, tablea1)
tablea1 <- select(tablea1, -Species)
tablea1 <- rename(tablea1, Species = six_let)
tablea1 <- select(tablea1, 'POE#', Location, 'Gross Area Infested (sq. m)', Zone)

tablea1_dt <- datatable(tablea1)

tablea1_dt
                     
```

### Table A-2 part 1 (a)
N sites surveyed, N of NIS Observed, N Sites w/NIS observed, N sites w/ NIS, N Sites w/o NIS, % Sites w/ NIS, % of Species Detected, Area Infestation = total area

```{r}
# Number of target species observed
spplist <- c(poe_clean$SCNTFC_CD, poe_clean$SCNTFC_CD2, poe_clean$SCNTFC_CD3, poe_clean$SCNTFC_CD4, poe_clean$SCNTFC_CD5)

N_sites_Surveyed <- as.numeric(length(unique(poe_clean_pivot$LOC_NM)))

N_of_NIS_Observed <- length(unique(na.omit(spplist))) - 1

NONEVal2 <- as.numeric(nrow(filter(poe_clean, SCNTFC_CD == "NONE")))

Sites_w_NIS <- N_sites_Surveyed - NONEVal2

Sites_wo_NIS <- NONEVal2

per_Sites_w_NIS <- round((Sites_w_NIS / N_sites_Surveyed)*100, 2)

per_of_Species_Detected <- (N_of_NIS_Observed/25) *100

# Fix rounding up above in poe_clean
Area_of_Infestation <- sum(poe_clean_pivot$Area)

tablea2a <- data.frame(N_sites_Surveyed, N_of_NIS_Observed, Sites_w_NIS, Sites_wo_NIS, per_Sites_w_NIS, per_of_Species_Detected, Area_of_Infestation)

table2a_dt <- datatable(tablea2a)
table2a_dt

```


### Species total area per year named table A-2 part 2 (b)
```{r}
tablea2b <- ungroup(tablea2)
tablea2b <- group_by(tablea2b, spp)
tablea2b <- summarize(tablea2b, sum(sumarea))
# select right key
spp_key_a2 <- select(spp_key, Scientific_name, USDA)
spp_key_a2 <- rename(spp_key_a2, spp = USDA)
# join to key
tablea2b <- right_join(spp_key_a2, tablea2b)
tablea2b$Park <- rep("SAMO", length(tablea2b$Scientific_name))
# rename and clean table
tablea2b <- rename(tablea2b, Species = Scientific_name, "Area Infestation [sq. m.]" = "sum(sumarea)")
tablea2b <- select(tablea2b, Park, Species, `Area Infestation [sq. m.]`)
tablea2b$`Area Infestation [sq. m.]` <- round(tablea2b$`Area Infestation [sq. m.]`)

tablea2b_dt <- datatable(tablea2b)
tablea2b_dt
  
```



### Most common target species at POEs and how many sites was it seen at
```{r}
poe_clean_pivot <- ungroup(poe_clean_pivot)
mostcomm <- group_by(poe_clean_pivot, LOC_NM, spp)
mostcomm <- summarise(mostcomm, sites = n())
mostcomm <- ungroup(mostcomm)
mostcomm <- select(mostcomm, LOC_NM, spp)
mostcomm <- group_by(mostcomm, spp)
mostcomm <- summarise(mostcomm, n = n())
mostcomm <- right_join(spp_key_a2, mostcomm)

print(slice_max(mostcomm, n))

```


### Out of the total number of sites how many had 1-5 and 6 or more
```{r}
# group to summarize
Numspp_poe2 <- unique(poe_clean_pivot[c("spp", "LOC_NM")])
Numspp_poe2 <- group_by(Numspp_poe2, LOC_NM)
Numspp_poe2 <- summarize(Numspp_poe2, spp = n())
Numspp_poe2 <- group_by(Numspp_poe2, spp)
Numspp_poe2 <- summarise(Numspp_poe2, sites = n())

# change these numbers to get different numbers relative to year
Numspp_one_to_five <- filter(Numspp_poe2, spp < 6)
Numspp_one_to_five <- sum(Numspp_one_to_five$sites)

Numspp_six_or_more <- filter(Numspp_poe2, spp > 5)
Numspp_six_or_more <- sum(Numspp_six_or_more$sites)

print(data.frame(Numspp_one_to_five, Numspp_six_or_more))

```



### Which location had the highest number of target invasives present and how many
*multiple returns if multiple sites with max value*
```{r}
highestspp <- group_by(poe_clean_pivot, LOC_NM, spp)
highestspp <- summarize(highestspp, n = n())
highestspp <- ungroup(highestspp)
highestspp <- group_by(highestspp, LOC_NM)
highestspp <- select(highestspp, LOC_NM, spp)
highestspp <- summarize(highestspp, spp_at_site = n())
highestspp <- right_join(highestspp, poe_loc_key)
highestspp <- rename(highestspp, POE = LOC_NM)

print(slice_max(highestspp, spp_at_site))

```



### Pie chart Figrue 4
Count of POEs with Different Number Classes of Target Invasive Species Detected

*NOTE: change value range for number classes depending on year*
Number Classes
0, 1-2, 3-5, 6-10
```{r}
# Change value ranges near end of chunk for POE pie graph

# group to summarize
Numspp_poe <- unique(poe_clean_pivot[c("spp", "LOC_NM")])
Numspp_poe <- group_by(Numspp_poe, LOC_NM)
Numspp_poe<- summarize(Numspp_poe, spp = n())
Numspp_poe<- group_by(Numspp_poe, spp)
Numspp_poe <- summarise(Numspp_poe, sites = n())

# go back and add sites with 0 found
NONEVal2 <- as.numeric(nrow(filter(poe_clean, SCNTFC_CD == "NONE")))

# add this value to Numspp
Numspp_poe <- rbind(Numspp_poe, list(0, NONEVal2))

# Make groups based on number change if values change
#################################### Specify Ranges here #####################################################
ranges <- c("0", rep("1-2", 2), rep("3-5", 3), rep("6-8", 3), rep("9-12", 2))

Numspp_poe <- Numspp_poe[order(Numspp_poe$spp),]

Numspp_poe <- cbind(Numspp_poe, ranges)

# Number of species in each range
Numspp_poe <- group_by(Numspp_poe, ranges)
Numspp_poe_range <- summarise(Numspp_poe, sitesum = sum(sites))

print(Numspp_poe_range)

# specify the factor levels in order
#################################### Specify Ranges here as well################################################## 
Numspp_poe_range$ranges <- factor(Numspp_poe_range$ranges, levels= c("0", "1-2", "3-5", "6-8", "9-12"))
Numspp_poe_range <- Numspp_poe_range[order(Numspp_poe_range$ranges),]


Numspp_poe_range2 <- Numspp_poe_range %>% 
  mutate(csum = rev(cumsum(rev(sitesum))), 
         pos = sitesum/2 + lead(csum, 1),
         pos = if_else(is.na(pos), sitesum/2, pos))

ggplot(Numspp_poe_range, aes(x = "" , y = sitesum, fill = ranges)) +
  geom_col(width = 1, color = 1)+
  coord_polar(theta = "y")+
  scale_fill_brewer(palette = "Spectral")+
  geom_label_repel(data = Numspp_poe_range2,
                   aes(y = pos, label = sitesum),
                   size = 4.5, nudge_x = 1, show.legend = FALSE)+
  guides(fill = guide_legend(title = "Number of Species")) +
  theme_void()

```

### Bar Chart Figure 4 ALT
```{r}
ggplot(Numspp_poe_range, aes(x = ranges , y = sitesum, fill = ranges))+
  geom_bar(stat = "identity")+
  theme_minimal()+
  geom_text(aes(label = sitesum), vjust = 2)

```


## Dirt Roads and Trails

### Make new dataframe to have how many times a number of species occurred at each site in DRT
```{r}

DRT_NNIS_SPPS <- data.frame(DRT_NNIS_raw$Location_Code, DRT_NNIS_raw$SpeciesName)

# Count number of times NONE appears
NONEVal <- length(DRT_NNIS_SPPS[which(DRT_NNIS_SPPS=="NONE"), 2])

DRT_NNIS_SPPS <- DRT_NNIS_SPPS[! grepl("NONE", DRT_NNIS_SPPS$DRT_NNIS_raw.SpeciesName), ]

DRT_NNIS_SPPS <- data.frame(Sp = DRT_NNIS_SPPS$DRT_NNIS_raw.SpeciesName, loc = DRT_NNIS_SPPS$DRT_NNIS_raw.Location_Code)

DRT_NNIS_SPPS<- as.data.frame(table(DRT_NNIS_SPPS$loc))

NSPP_persite <- data.frame(table(DRT_NNIS_SPPS$Freq))
NSPP_persite$Var1 <- as.numeric(NSPP_persite$Var1)

NSPP_persite[nrow(NSPP_persite)+1,] <- c(0, NONEVal)

NSPP_persite <- rename(NSPP_persite, numspp = Var1, numsites = Freq)

print(NSPP_persite)

```

### Pie chart Figure 5
Count of DRTs with different numbers of Target Species detected
* include numbers in each slide of pie *
```{r}
# Make each of the numbers into a ratio
NSPP_persite$ratio <- NSPP_persite$numsites / sum(NSPP_persite$numsites) *100

# make a factor again
NSPP_persite$numspp <- as.factor(NSPP_persite$numspp)

# label positions

# Create Data
data <- data.frame(
  group=LETTERS[1:5],
  value=c(13,7,9,21,2)
)


# Compute the position of labels
NSPP_persite <- NSPP_persite %>% 
  arrange(desc(numspp)) %>%
  mutate(prop = numsites / sum(NSPP_persite$numsites) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )


# make chart with values inside
ggplot(NSPP_persite, aes(x="", y=ratio, fill=numspp)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0)+
  theme_void()+
  geom_text(aes(y=ypos, label=numsites), color="black", size=6)+
  scale_fill_brewer(palette="Set1")

# Outside
NSPP_persite2 <- NSPP_persite %>% 
  mutate(csum = rev(cumsum(rev(ratio))), 
         pos = ratio/2 + lead(csum, 1),
         pos = if_else(is.na(pos), ratio/2, pos))

# round up values
perc <- round(NSPP_persite$ratio, 2)

ggplot(NSPP_persite, aes(x = "" , y = ratio, fill = fct_inorder(numspp))) +
  geom_col(width = 1, color = 1) +
  coord_polar(theta = "y") +
  # Can change color in palette = 
  scale_fill_brewer(palette = "Spectral") +
  geom_label_repel(data = NSPP_persite2,
                   aes(y = pos, label = numsites),
                   size = 4.5, nudge_x = 1, show.legend = FALSE) +
  guides(fill = guide_legend(title = "Number of Species")) +
  theme_void()


```

# Barchart DRT Figure 5 ALT
```{r}
ggplot(NSPP_persite, aes(x = numspp , y = numsites, fill = numsites))+
  geom_bar(stat = "identity")+
  theme_minimal()+
  geom_text(aes(label = numsites), vjust = 2)
```

# Table B-2
```{r}

tableb1 <- select(DRT_NNIS_raw, Location_Code, Loc_Name, SpeciesName, X0, X1, X2, X3, X4, X5, X6, X7, X8, X9, X10)
tableb1$Location_Code <- gsub("GRTS", "DRT", tableb1$Location_Code)
tableb1 <- rename(tableb1, DRT = Location_Code, Location = Loc_Name, 'Species Code'= SpeciesName)

tableb1_dt <- datatable(tableb1)
tableb1_dt

```



### Total Sites visited this year
```{r}
print(length(unique(DRT_NNIS_raw$Location_Code)))

```


### How many of the total target species were found on DRTs
```{r}
# Include -1 since none is a value
print(length(unique(DRT_NNIS_raw$SpeciesName)) -1)

```

### _ of the total sites had at least one species
```{r}
print(sum(NSPP_persite$numsites) - NSPP_persite[NSPP_persite$numspp == 0, 2])

```


### how many had one and two species found at site
```{r}

print(NSPP_persite[NSPP_persite$numspp == 2, 2] + NSPP_persite[NSPP_persite$numspp == 1, 2])

```


### Most common target invasive and at how many sites
```{r}

print(tail(sort(table(DRT_NNIS_raw$SpeciesName), deceasing=T), n=1))

```


# Extras and possible future questions

### _ target invasive species were found across _ vegmon sites

### Among the _ sites we surveyed

### Greatest number of sites for any one non-native species

### Number of points of contact for vegmon (%cover) 
One point of contact = 1% so # of hits is the % cover for that plot

### DRT Location Key
```{r}
# Make DRT location key
drt_loc_key <- DRT_NNIS_raw
drt_loc_key$Location_Code <- gsub("GRTS", "DRT", drt_loc_key$Location_Code)
drt_loc_key <- na.omit(unique(select(drt_loc_key, Location_Code, Loc_Name)))

```


### Calculating Percent Cover by Rows Potential VegMon
Not necessary but may be useful for vegmon code
```{r}
DRT_NNIS_raw$count_na <- rowSums(is.na(DRT_NNIS_raw))
DRT_NNIS_raw$NHits <- 11 - DRT_NNIS_raw$count_na
DRT_NNIS_raw$percent_cover <- DRT_NNIS_raw$NHits *10

```















